Stability

### 2022-09-28 Rmd/Stability.Rmd
added plots

For each plant species per site, stability (inverse of the coefficient of variation) of the visitation rate of pollinators (visitation rate calculated like frequency/flower abundance) and also of the fruit proportion and the seed numbers were calculated. Total of pollinator richness (sum) was obtained and furthermore, the log of variance ratio (Lepš et al., 2018) and Loreau & Mazancourt syncrony index were calculated.

```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(kableExtra)
library(reshape2)

Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") #400 observaciones
Pollinator_Plant<-Pollinator_Plant[,-1]

@@

@@

@@

# join tables 
full2=full_join(cv_1Fruit2, cv_1Seed2, by = c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., cv_1pollinator2, by=c('Plant_gen_sp', 'Site_ID')) %>%
  full_join (., S2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds, cv_1_visitation=visitatio_rate)

@@

tr2<-full2 %>% select(cv_1_fruit, cv_1_seed,cv_1_visitation,richness)

@@

# correlacion con nuevos calculos (full2 = sin plant_id)
b<-full2 %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,richness,log_VR,syncLM)

@@

@@

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
# 4 plant species are in 2-3 site (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)

@@

sta_fruit<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

@@

@@

A- Richness ~ log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(richness~log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(richness~log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(richness~log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = richness),shape=20)+ 
  labs(x = "log_VR",y="richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = richness),shape=20)+ 
  labs(x = "log_VR",y="richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = richness),shape=20)+ 
  labs(x = "log_VR",y="richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = richness),shape=20)+ 
  labs(x = "log_VR",y="richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = richness),shape=20)+ 
  labs(x = "log_VR",y="richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = richness),shape=20)+ 
  labs(x = "log_VR",y="richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = richness),shape=20)+ 
  labs(x = "log_VR",y="richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

\newpage
A- Richness ~ Loreau & Mazancourt syncrony index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich2<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(richness~syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

#goodness of fit measures
rich2_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(richness~syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(richness~syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = richness),shape=20)+ 
  labs(x = "syncLM",y="richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = richness),shape=20)+ 
  labs(x = "syncLM",y="richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = richness),shape=20)+ 
  labs(x = "syncLM",y="richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = richness),shape=20)+ 
  labs(x = "syncLM",y="richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = richness),shape=20)+ 
  labs(x = "syncLM",y="richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = richness),shape=20)+ 
  labs(x = "syncLM",y="richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = richness),shape=20)+ 
  labs(x = "syncLM",y="richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

A) richness + log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model 1: richness + log VR
sta_polli<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

#goodness of fit measures
sta_polli_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

# model plot (cv_1_visitation~richness)
sta_polli2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "richness"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

>>>>

Plots of fruit proportion and year for each plant species and site

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(reshape2)
library(tidyr)
library(ggplot2)
#install.packages("ggeffects")
library(ggeffects)
library(patchwork)
library(ggcorrplot)
library(ggpubr)
library(kableExtra)

Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

@@

pol_plant2$Year <- factor(pol_plant2$Year)

plots3 <- pol_plant2 %>%
group_by(Plant_gen_sp) %>%
group_map(~ ggplot(.) + aes(x=Year, y=fruit_proportion, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]]))

ggarrange(plots3[[1]],plots3[[2]],plots3[[3]],plots3[[4]],plots3[[5]],plots3[[6]], plots3[[7]],plots3[[8]],plots3[[9]],plots3[[10]],plots3[[11]],plots3[[12]],ncol=3,nrow = 4)

Plots of seed number and year for each plant species and site

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

plots3_seed <- pol_plant2 %>%
group_by(Plant_gen_sp) %>%
group_map(~ ggplot(.) + aes(x=Year, y=Seeds, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]]))

ggarrange(plots3_seed[[1]],plots3_seed[[2]],plots3_seed[[3]],plots3_seed[[4]],plots3_seed[[5]],plots3_seed[[6]],plots3_seed[[7]],plots3_seed[[8]],plots3_seed[[9]],plots3_seed[[10]],plots3_seed[[11]],plots3_seed[[12]],ncol=3,nrow = 4)

Plots of visitation rate and year for each plant species and site

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}

plots3_visitation_rate <- pol_plant2 %>%
group_by(Plant_gen_sp) %>%
group_map(~ ggplot(.) + aes(x=Year, y=visitatio_rate, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]]))

ggarrange(plots3_visitation_rate[[1]],plots3_visitation_rate[[2]],plots3_visitation_rate[[3]],plots3_visitation_rate[[4]],plots3_visitation_rate[[5]],plots3_visitation_rate[[6]],plots3_visitation_rate[[7]],plots3_visitation_rate[[8]],plots3_visitation_rate[[9]],plots3_visitation_rate[[10]],plots3_visitation_rate[[11]],plots3_visitation_rate[[12]],ncol=3,nrow = 4)

\newpage
For each plant species per site, stability (inverse of the coefficient of variation) of the visitation rate of pollinators (visitation rate calculated like frequency/flower abundance) and also of the fruit proportion and the seed numbers were calculated. Pollinator richness (total and mean) was obtained and furthermore, the log of variance ratio (Lepš et al., 2018) and Loreau & Mazancourt syncrony index were calculated.

```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

@@

#  pollinator richness for each plant species per site (Total)
S<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = Pollinator_Plant,FUN = sum)

@@

# join tables 
full2=full_join(cv_1Fruit2, cv_1Seed2, by = c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., cv_1pollinator2, by=c('Plant_gen_sp', 'Site_ID')) %>%
  full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., S2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds,   cv_1_visitation=visitatio_rate,S_total=richness.x, S_mean=richness.y)

@@

tr2<-full2 %>% select(cv_1_fruit, cv_1_seed,cv_1_visitation,S_total, S_mean)

@@

# correlacion con nuevos calculos (full2 = sin plant_id)
b<-full2 %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,S_total,S_mean,log_VR,syncLM)

@@

Replace Inf and -Inf with NA

@@

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

# 4 plant species are in 2-3 site (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)

@@

#plot
plots_sta_fruit <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=cv_1_visitation, y=cv_1_fruit) + 
 theme_bw()+ geom_point(size = 5) + labs(x = "visitation rate  stability",y="fruit proportion stability")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

ggarrange(plots_sta_fruit[[1]],plots_sta_fruit[[2]],plots_sta_fruit[[3]],plots_sta_fruit[[4]],plots_sta_fruit[[5]],plots_sta_fruit[[6]],plots_sta_fruit[[7]], ncol=3, nrow=3)

Halimium calycinum only one observation

Summary of model per plant species

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

#model
sta_fruit<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

checking residuals, I detect problems with the homogeneity of variance for all plant species

@@

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

#plot
plots_sta_seed <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=cv_1_visitation, y=cv_1_seed) + 
 theme_bw()+ geom_point(size = 5) + labs(x = "visitation rate  stability",y="seed stability")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

ggarrange(plots_sta_seed[[1]],plots_sta_seed[[2]],plots_sta_seed[[3]],plots_sta_seed[[4]],plots_sta_seed[[5]],plots_sta_seed[[6]],plots_sta_seed[[7]], ncol=3, nrow=3)

Summary of model

@@

A- Total richness ~ log VR

```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

#plot
plots_rich <- full_2 %>%
  group_by(Plant_gen_sp) %>%
  group_map(~ ggplot(.) + aes(x=log_VR, y=S_total) + 
 theme_bw()+ geom_point(size = 5) + labs(x = "log VR",y="Total richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))

ggarrange(plots_rich[[1]],plots_rich[[2]],plots_rich[[3]],plots_rich[[4]],plots_rich[[5]],plots_rich[[6]],plots_rich[[7]], ncol=3, nrow=3)

rich<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

rich_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.1 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_total),shape=20)+ 
  labs(x = "log_VR",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

\newpage
B- total richness ~ Loreau & Mazancourt syncrony index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich2<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

#goodness of fit measures
rich2_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

rich.2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_total~syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_total),shape=20)+ 
  labs(x = "syncLM",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

C- mean richness ~ log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich3<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich3<-rich3 %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich3 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich3$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

rich3_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table5<-rich3_glance %>%
  mutate(Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

rich.3 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.3$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.3$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.3$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_mean),shape=20)+ 
  labs(x = "log_VR",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

D- mean richness ~ Loreau & Mazancourt syncrony index
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

rich4<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

rich4<-rich4 %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

rich4 %>% 
 kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
column_spec(6, bold = ifelse(rich4$p.value < 0.05, T, F) )%>%
  kable_styling(position="center", latex_option="hold_position")

rich4_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table6<-rich4_glance %>%
  mutate(Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))

rich.4 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))

p1=rich.4$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))

p2=rich.4$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))

p3=rich.4$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))

p4=rich.4$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))

p5=rich.4$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))

p6=rich.4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))

p7=rich.4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_mean),shape=20)+ 
  labs(x = "syncLM",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))

@@

A) total richness + log VR
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

#model 1: richness + log VR
sta_polli<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

@@

#goodness of fit measures
sta_polli_glance<-full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

@@

# model plot (cv_1_visitation~richness)
sta_polli2 <- full_2 %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
